Computer-Assisted Analysis of the \\ Anderson-Hájek Ontological Controversy

### 2017-01-06 Papers/2017/LogicaUniversalis-HajekAndersonControversy/main.tex
Add missing dashes

\begin{figure}
\begin{sideways}
%\includegraphics[width=1.2\textwidth]{Summary.png} 
\end{sideways}
%
\begin{sideways}
%\scalebox{.9}{
\resizebox{19cm}{4.5cm}{
\begin{tabular}{lccccccccccccc} 
\toprule
Investigated Variant & D1$'$ & A:A1$'$ & A2$'$ & A3$'$ & A4 & A4$'$ & H:A4 & A5 & A5$'$
  & H:A5 & T3 & T3$'$ & MC \\  
\midrule 
Scott (const) & - & - & - & - & \tabboxs{\tabred}{N/I} & - & - & \tabboxs{\tabred}{N/I} & - & - & P & -  & P \\
Scott (var) & - & - & - & - & \tabboxs{\tabred}{N/I} & - & - & \tabboxs{\tabred}{N/I} & - & - & P & -  & P \\
Anderson (const) & - & - & - & - & \tabbox{\tabred}{R(K4B)} & - & - & - & \tabboxs{\tabred}{R}  & - & - & P  & CS \\
Anderson (var) & - & - & - & - & \tabbox{\tabred}{R(K4B)} & - & - & - & \tabboxs{\tabred}{R}  & - & - & P  & CS \\
Anderson (mix) & - & - & - & - & \tabbox{\tabred}{R(K4B)} & - & - & - & \tabboxs{\tabred}{I}  & - & - & \tabboxs{\tabred}{CS} & CS \\
H\'ajek AOE$'$ (var) & - & - & \tabboxs{\tabyellow}{CS}  &  & \tabboxs{\tabred}{S/I} & - & - & - & \tabboxs{\tabred}{S/I}  & - & - & P(KB) & CS \\
H\'ajek AOE$'$\_0 (var) & - & - & - & \tabboxs{\tabyellow}{CS} & \tabboxs{\tabgreen}{R} & - & - & - & S/U & - & - & P(KB) & CS \\
H\'ajek AOE$''$ (var) & - & - &  &  & - & - & \tabboxs{\tabred}{S/I} & - & - & \tabboxs{\tabred}{S/I} & - & P(KB) & CS \\
Anderson (simp) (var) & - & R & R  &  &  & R(K4B) & - & - & & - & - &  & \\
Bjørdal (const) & \tabbox{\tabgreen}{R(K4)} & - & \tabboxs{\tabgreen}{R} & \tabboxs{\tabgreen}{R} & - & \tabbox{\tabgreen}{R(KT)} & - & - &\tabboxs{\tabyellow}{N/I} & - & - & \tabbox{\tabgreen}{P(KB)} &  CS \\
Bjørdal (var) & \tabboxs{\tabyellow}{CS} & - & \tabboxs{\tabgreen}{R} & \tabboxs{\tabgreen}{R} & - & \tabbox{\tabgreen}{R(KT)} & - & - &\tabboxs{\tabyellow}{N/I} & - & - & \tabbox{\tabgreen}{P(KB)} &  CS \\
\bottomrule
\end{tabular}
}
\end{sideways}
\caption{Summary of Results.}
\label{fig:summary}
\end{figure}

Figure \ref{fig:summary} summarizes the results obtained by the
automated reasoning tools. The following abbreviations are used: S/I =
superfluous and independent; R = superfluous and redundant; S/U =
superfluous and unknown whether redundant or independent; N/I =
non-superfluous and independent; P = provable; CS =
counter-satisfiable. The weakest logic required to show redundancy or
provability is indicated in parentheses (\K is the default).  Cells
highlighted in \colorbox{\tabred}{red} contain results that differ
from what had been claimed by either Magari, Anderson or Hájek. Cells
highlighted in \colorbox{\tabyellow}{yellow} contain results that are
surprising, albeit not contradicting any claims. Cells highlighted in
\colorbox{\tabgreen}{green} contain results where the tools were able
to obtain the same results as humans, but using weaker modal logics.
\footnote{EDNOTE: What is the difference between - and empty cells?}

>>>>

\begin{figure}
\begin{sideways}
%\includegraphics[width=1.2\textwidth]{Summary.png} 
\end{sideways}
%
\begin{sideways}
%\scalebox{.9}{
\resizebox{19cm}{4.5cm}{
\begin{tabular}{lccccccccccccc} 
\toprule
Investigated Variant & D1$'$ & A:A1$'$ & A2$'$ & A3$'$ & A4 & A4$'$ & H:A4 & A5 & A5$'$
  & H:A5 & T3 & T3$'$ & MC \\  
\midrule 
Scott (const) & - & - & - & - & \tabboxs{\tabred}{N/I} & - & - & \tabboxs{\tabred}{N/I} & - & - & P & -  & P \\
Scott (var) & - & - & - & - & \tabboxs{\tabred}{N/I} & - & - & \tabboxs{\tabred}{N/I} & - & - & P & -  & P \\
Anderson (const) & - & - & - & - & \tabbox{\tabred}{R(K4B)} & - & - & - & \tabboxs{\tabred}{R}  & - & - & P  & CS \\
Anderson (var) & - & - & - & - & \tabbox{\tabred}{R(K4B)} & - & - & - & \tabboxs{\tabred}{R}  & - & - & P  & CS \\
Anderson (mix) & - & - & - & - & \tabbox{\tabred}{R(K4B)} & - & - & - & \tabboxs{\tabred}{I}  & - & - & \tabboxs{\tabred}{CS} & CS \\
H\'ajek AOE$'$ (var) & - & - & \tabboxs{\tabyellow}{CS}  &  & \tabboxs{\tabred}{S/I} & - & - & - & \tabboxs{\tabred}{S/I}  & - & - & P(KB) & CS \\
H\'ajek AOE$'$\_0 (var) & - & - & - & \tabboxs{\tabyellow}{CS} & \tabboxs{\tabgreen}{R} & - & - & - & S/U & - & - & P(KB) & CS \\
H\'ajek AOE$''$ (var) & - & - & - & - & - & - & \tabboxs{\tabred}{S/I} & - & - & \tabboxs{\tabred}{S/I} & - & P(KB) & CS \\
Anderson (simp) (var) & - & R & R  & - & - & R(K4B) & - & - & - & - & - & - & - \\
Bjørdal (const) & \tabbox{\tabgreen}{R(K4)} & - & \tabboxs{\tabgreen}{R} & \tabboxs{\tabgreen}{R} & - & \tabbox{\tabgreen}{R(KT)} & - & - &\tabboxs{\tabyellow}{N/I} & - & - & \tabbox{\tabgreen}{P(KB)} &  CS \\
Bjørdal (var) & \tabboxs{\tabyellow}{CS} & - & \tabboxs{\tabgreen}{R} & \tabboxs{\tabgreen}{R} & - & \tabbox{\tabgreen}{R(KT)} & - & - &\tabboxs{\tabyellow}{N/I} & - & - & \tabbox{\tabgreen}{P(KB)} &  CS \\
\bottomrule
\end{tabular}
}
\end{sideways}
\caption{Summary of Results.}
\label{fig:summary}
\end{figure}

Figure \ref{fig:summary} summarizes the results obtained by the
automated reasoning tools. The following abbreviations are used: S/I =
superfluous and independent; R = superfluous and redundant; S/U =
superfluous and unknown whether redundant or independent; N/I =
non-superfluous and independent; P = provable; CS =
counter-satisfiable. The weakest logic required to show redundancy or
provability is indicated in parentheses (\K is the default).  Cells
highlighted in \colorbox{\tabred}{red} contain results that differ
from what had been claimed by either Magari, Anderson or Hájek. Cells
highlighted in \colorbox{\tabyellow}{yellow} contain results that are
surprising, albeit not contradicting any claims. Cells highlighted in
\colorbox{\tabgreen}{green} contain results where the tools were able
to obtain the same results as humans, but using weaker modal logics.
